Congestion Control Aware Queuing

### 2019-10-21 tex/paper.tex
Reduce fig size

\begin{figure}[h]
\subfloat[Throughput of the fq \gls{qdisc}\label{fig:fqThroughput}
]{\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}}{}
\subfloat[Delay of the fq \gls{qdisc}.\label{fig:fqDelay}
]{\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}}{}
\caption{Throughput (\ref{fig:fqThroughput}) and delay (\ref{fig:fqDelay}) of a Cubic flow that is managed by fq at the bottleneck. The initial bandwidth is 20\,Mbit/s but it is halved after 30\,s. The delay is 10\,ms. It is clear that there is a standing queue and after the bandwidth halves, the minimum delay is 100\,ms even though 10\,ms would be the possible.}
\label{fig:fq}
\end{figure}

@@

\begin{figure}[h]
\subfloat[Throughput of the fq\_codel \gls{qdisc}\label{fig:fqCodelThroughputLong}
]{\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}}{}
\subfloat[Delay of the fq\_codel \gls{qdisc}.\label{fig:fqCodelDelayLong}
]{\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}}{}
\caption{Throughput (\ref{fig:fqCodelThroughputLong}) and delay (\ref{fig:fqCodelDelayLong}) of a Cubic flow that is managed by fq\_codel at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 101.36\,ms. Total throughput is 2615\,MB.}
\label{fig:fqCodel}
\end{figure}

\begin{figure}[h]
\subfloat[Throughput of our \gls{qdisc}\label{fig:cnThroughputLong}
]{\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}}{}
\subfloat[Delay of our \gls{qdisc}.\label{fig:cnDelayLong}
]{\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}}{}
\caption{Throughput (\ref{fig:cnThroughputLong}) and delay (\ref{fig:cnDelayLong}) of a Cubic flow that is managed by our \gls{qdisc} at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 129.45\,ms. Total throughput is 2893\,MB.}
\label{fig:cnLong}
\end{figure}

Next we compare our \gls{qdisc} against fq\_codel. Figure\autoref{fig:fqCodelDelayLong} shows that fq\_codel keeps the queuing delay under 5\,ms. Figure\autoref{fig:fqCodelThroughputLong} shows that keeping the queuing delay that low is detrimental for achieving full throughput when using the Cubic \gls{cca}. With our \gls{qdisc} we achieve throughput that is more than 10\% higher overall, while only slightly increasing the average delay. In addition to Cubic, we performed experiments with Reno. Here, over a 240\,s flow of 100\,Mbit/s with a delay of 50\,ms, our \gls{qdisc} achieves more than 20\% higher throughput than fq\_codel. The average \gls{rtt} for fq\_codel is 51.13\,ms while it is 96.59\,ms for our \gls{qdisc}.

Besides fq\_codel possibly leading to lower throughput as we have shown, another problem is that for links with a small \gls{bdp} fq\_codel can keep a standing queue akin to fq since fq\_codel only wants queuing delay to fall below 5\,ms once every 100\,ms. For example, on a link with a base \gls{rtt} of 5\,ms, fq\_codel would accept a permanent standing queue of 4.9\,ms, leading to overall \gls{rtt} being doubled.

@@

Our goal was to design a \gls{qdisc} which achieves maximum throughput while keeping the queuing delay as small as possible. The results of the experiments, which we perform with a prototype of our \gls{qdisc}, show that there are certain common scenarios in which current state-of-the-art \glspl{qdisc} like fq, fq\_codel and cake fall short of the optimum throughput by a significant margin while our approach succeeds in leading to full utilization of the link at the bottleneck. Furthermore, the aforementioned \glspl{qdisc} also suffer from standing delays is certain scenarios which we can also mitigate with our approach.

>>>>

\begin{figure}[h]
%\subfloat[Throughput of the fq \gls{qdisc}\label{fig:fqThroughput}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
%\subfloat[Delay of the fq \gls{qdisc}.\label{fig:fqDelay}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow that is managed by fq at the bottleneck. The initial bandwidth is 20\,Mbit/s but it is halved after 30\,s. The delay is 10\,ms. It is clear that there is a standing queue and after the bandwidth halves, the minimum delay is 100\,ms even though 10\,ms would be the possible.}
\label{fig:fq}
\end{figure}

@@

\begin{figure}[h]
\subfloat[Throughput of the fq\_codel \gls{qdisc}\label{fig:fqCodelThroughputLong}
]{\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}}{}
\subfloat[Delay of the fq\_codel \gls{qdisc}.\label{fig:fqCodelDelayLong}
]{\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}}{}
\caption{Throughput (\ref{fig:fqCodelThroughputLong}) and delay (\ref{fig:fqCodelDelayLong}) of a Cubic flow that is managed by fq\_codel at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 101.61\,ms. Total throughput is 2615\,MB.}
\label{fig:fqCodel}
\end{figure}

\begin{figure}[h]
\subfloat[Throughput of our \gls{qdisc}\label{fig:cnThroughputLong}
]{\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}}{}
\subfloat[Delay of our \gls{qdisc}.\label{fig:cnDelayLong}
]{\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}}{}
\caption{Throughput (\ref{fig:cnThroughputLong}) and delay (\ref{fig:cnDelayLong}) of a Cubic flow that is managed by our \gls{qdisc} at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 130.36\,ms. Total throughput is 2893\,MB.}
\label{fig:cnLong}
\end{figure}

Next we compare our \gls{qdisc} against fq\_codel. Figure\autoref{fig:fqCodelDelayLong} shows that fq\_codel keeps the queuing delay under 5\,ms. Figure\autoref{fig:fqCodelThroughputLong} shows that keeping the queuing delay that low is detrimental for achieving full throughput when using the Cubic \gls{cca}. With our \gls{qdisc} we achieve throughput that is more than 10\% higher overall, while only slightly increasing the average delay. In addition to Cubic, we performed experiments with Reno. Here, over a 240\,s flow of 100\,Mbit/s with a delay of 50\,ms, our \gls{qdisc} achieves more than 20\% higher throughput than fq\_codel. The average \gls{rtt} for fq\_codel is 51.34\,ms while it is 96.78\,ms for our \gls{qdisc}.

Besides fq\_codel possibly leading to lower throughput as we have shown, another problem is that for links with a small \gls{bdp} fq\_codel can keep a standing queue akin to fq since fq\_codel only wants queuing delay to fall below 5\,ms once every 100\,ms. For example, on a link with a base \gls{rtt} of 5\,ms, fq\_codel would accept a permanent standing queue of 4.9\,ms, leading to overall \gls{rtt} being doubled, which is not required for achieving optimal throughput.

@@

Our goal was to design a \gls{qdisc} which achieves maximum throughput while keeping the queuing delay as small as possible. The results of the experiments, which we perform with a prototype of our \gls{qdisc}, show that there are certain common scenarios in which current state-of-the-art \glspl{qdisc} like fq, fq\_codel and cake fall short of the optimum throughput by a significant margin while our approach succeeds in leading to full utilization of the link at the bottleneck (with a potential increase in delay). Furthermore, the aforementioned \glspl{qdisc} also suffer from standing queues in scenarios with small \gls{bdp} which we can also mitigate with our approach.
